---
title: "Distances"
output: html_notebook
---

```{r}
library(tidyverse)
```


Given two vectors:

* p = number of variables that are positive for both instances
* q = number of variables that are positive for the $i_th$ object and negative for the $j_th$ object
* r = number of variables that are negative for the $i_th$ object and positive for the $j_th$ object
* s = number of variables that are positive for both instances
* $t = p + q + r + s$


# Distance for binary variables

```{r}
i <- factor("yes", "no", "yes", "no", "yes")
j <- factor("no", "yes", "no", "no", "yes")
```

```{r}
tribble(i, j)
```


## Simple matching distance

Useful when both positive and negative values carry equal information. Counts the number of times that both are different (one positive and the other negative).

$$d_{ij} = \frac{q+r}{p + q + r + s} = \frac{q+r}{t}$$

## Jaccard's distance

$$d_{ij} = \frac{q+r}{p + q + r}$$

## Hamming distance

Measures the leven of disagreement between two vectors. Count the number if digits in positions where they have a different digit. Distance is higher for values with bigger number of categories.

$$d_{ij} = q + r$$

## Simple matching coefficient

Useful when both positive and negative values carry equal information. Counts the number of times that both are equals (both positive or both negative)

$$d_{ij} = \frac{p+s}{p + q + r + s} = \frac{p+s}{t}$$

## Jaccard's coefficient

$$d_{ij} = \frac{p}{p + q + r} = \frac{p}{p + q + r}$$

# Distance for nominal variables


# Distance for ordinal variables

## Normalized Rank Transformation

## Spearman Distance

## Footrule Distance

## Kendall Distance

## Cayley Distance

## Hamming Distance

## Ulam Distance

## Chebyshev/Maximum distance

## Miskowski Distance


# Distance for quantitative variables

