---
title: "Distances"
output: html_notebook
---

```{r}
library(tidyverse)
```

For similarity in [0, 1] when 1 is exactly similar the dissimilarity is zero when the similarity is zero, i.e. very different, the dissimilarity is one.

$$s_{ij} = 1 - d_{ij}$$

If the value of similarity has range of -1 to +1 and the dissimilarity is measured with range 0 and 1 then:

$$s_{ij} = 1 - 2d_{ij}$$

because when the dissimilarity is one i.e. very different the similarity is minus one and when the dissimilarity is zero i.e. very similar the similarity is 1-


# Distance for binary variables


Given two vectors:

* p = number of variables that are positive for both instances
* q = number of variables that are positive for the $i_th$ object and negative for the $j_th$ object
* r = number of variables that are negative for the $i_th$ object and positive for the $j_th$ object
* s = number of variables that are positive for both instances
* $t = p + q + r + s$

| i / j | Yes | No |
|-------|-----|----|
| Yes   | p   | q  |
| No    | r   | s  |

```{r}
i <- factor(c("yes", "no", "yes", "no", "yes"), levels = c("yes", "no"))
j <- factor(c("no", "yes", "no", "no", "yes"), levels = c("yes", "no"))
```

```{r}
table(i, j)
```

```{r}
createTable <- function(i, j) {
  vtable <- list()
  vtable$table <- table(i, j)
  vtable$p <- vtable$table[1, 1]
  vtable$q <- vtable$table[1, 2]
  vtable$r <- vtable$table[2, 1]
  vtable$s <- vtable$table[2, 2]
  vtable
}
```


## Simple matching 

Useful when both positive and negative values carry equal information. Counts the number of times that both are different (one positive and the other negative).

### Coefficient (SMC)

$$s_{ij} = \frac{p+s}{p + q + r + s} = \frac{p+s}{t}$$

### Distance (SMD)

$$d_{ij} = 1-s_{ij} = 1 - \frac{p+s}{p + q + r + s} = \frac{q+r}{p + q + r + s} = \frac{q+r}{t}$$

```{r}
simple_matching_distance <- function(i, j) {
  d <- createTable(i, j)
  t <- d$p + d$q + d$r + d$s
  return((d$q + d$r) / t)
}
```

```{r}
simple_matching_distance(i, j)
```

Note that $q+r$ is the Hamming Distance.

## Jaccard's

Measurement of **asymmetric information** on binary and non-binary variables.

When the existence of s (number of variables that are negative for both objects) makes no sense becase it represents a double absence, this is a good metric. This is because the value of positive and negative values of a variable have no equal information (asymmetry).  

### Coefficient

Jaccard's coefficient measures similarity

$$s_{ij} = \frac{p}{p+q+r}$$

### Distance

Jaccard's distance measures dissimilarity

$$d_{ij} = \frac{q+r}{p + q + r}$$
```{r}
jaccard_distance <- function(i, j) {
  d <- createTable(i, j)
  return((d$q + d$r) / (d$p + d$q + d$r))
}
```

### Non binary data



## Hamming distance

Measures the leven of disagreement between two vectors. Count the number if digits in positions where they have a different digit. Distance is higher for values with bigger number of categories.

$$d_{ij} = q + r$$

## Simple matching coefficient

Useful when both positive and negative values carry equal information. Counts the number of times that both are equals (both positive or both negative)

$$d_{ij} = \frac{p+s}{p + q + r + s} = \frac{p+s}{t}$$

## Jaccard's coefficient

$$d_{ij} = \frac{p}{p + q + r} = \frac{p}{p + q + r}$$

# Distance for nominal variables


# Distance for ordinal variables

## Normalized Rank Transformation

## Spearman Distance

## Footrule Distance

## Kendall Distance

## Cayley Distance

## Hamming Distance

## Ulam Distance

## Chebyshev/Maximum distance

## Miskowski Distance


# Distance for quantitative variables

