---
title: "Datasets"
output:
  html_document: default
---

```{r message=FALSE, warning=FALSE, include=FALSE}

path_to_data <- ".."
source("../data/load_data.R")
source("../data/show_data.R")
knitr::opts_chunk$set(out.width="100%")
```

## List

* **Binary**
  * Categorical attributes
    * Less than 10 attributes
      * [Breast Cancer](#Breast-Cancer)
      * [Cars](#Cars)
      * [Somerville](#Somerville)
      * [Tic-Tac-Toe](#Tic-Tac-Toe)
    * 10 or more attributes
  * Mixed: categorical and numerical attributes
    * Less than 10 attributes
      * [Caesarean](#Caesarean)
      * [Mammographic masses](#mammographic)
    * 10 or more attributes
      * [Travel Insurance](#Travel-insurance)
  * Numeric attributes
    * Less than 10 attributes
      * [Banknote authentication](#Banknote)
      * [Haberman's Survival](#Haberman)
      * [Skin segmentation](#Skin)
      * [Vertebral column 2](#Vertebral-column-2)
      * [Weight, height, gender](#Weight-height-gender)
    * 10 or more attributes
      * [Sonar](#sonar)
* **Multiclass**
  * Categorical attributes
    * Less than 10 attributes
      * [Balance Scale](#Balance-Scale)
      * [Chess](#Chess)
      * [Post-operative](#Post-operative)
    * 10 or more attributes
      * [Connect 4](#Connect4)
      * [Poker hand](#Poker-hand)
      * [Primary tumor](#Primary-tumor)
      * [Soybean](#Soybean)
      * [Zoo](#Zoo)
  * Mixed: categorical and numerical attributes
    * Less than 10 attributes
      * [Teaching assistant](#Teaching-assistant)
    * 10 or more attributes
  * Numeric attributes
    * Less than 10 attributes
      * [Ecoli](#ecoli)
      * [Iris](#iris)
      * [Life expectancy](#Life-expectancy)
      * [Seeds](#Seeds)
      * [Vertebral column 3](#Vertebral-column) https://archive.ics.uci.edu/ml/datasets/Vertebral+Column
    * 10 or more attributes

## Binary

### Categorical attributes

#### Less than 10 attributes

##### Breast Cancer {#Breast-Cancer}

<!-- Binary > Categorical > Less than 10 attributes --> 

This is one of three datasets provided by the Oncology Institute that has repeatedly appeared in the machine learning literature.

This data set includes 201 instances of one class and 85 instances of another class. The instances are described by 9 attributes. In this version of the dataset all the attributes are nominal.

* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Breast+Cancer)
* __Number of rows__: `r nrow(breast_cancer)`
* __Number of attributes__: `r ncol(breast_cancer) - 1`

__Description of the attributes:__

```{r echo=FALSE}
plot_dist_cols(breast_cancer)
```


##### Cars {#Cars}

<!-- Binary > Categorical > Less than 10 attributes --> 

Car Evaluation Database was derived from a simple hierarchical decision mode. The attributes include: buying price, maint price of the maintenance, number of doors, persons capacity in terms of persons to carry, lug_boot the size of luggage boot, safety estimated safety of the car and class. The class is the car acceptability and its possible values are: unacc, acc, good, vgood.

* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Car+Evaluation)
* __Number of rows__: `r nrow(cars)`
* __Number of attributes__: `r ncol(cars) - 1`

__Description of the attributes:__

```{r echo=FALSE}
plot_dist_cols(cars)
```

##### Somerville {#Somerville}

<!-- Binary > Categorical > Less than 10 attributes --> 

The skin dataset is collected by randomly sampling B,G,R values from face images of various age groups (young, middle, and old), race groups (white, black, and asian), and genders obtained from FERET database and PAL database. Total learning sample size is 245057; out of which 50859 is the skin samples and 194198 is non-skin samples. Color FERET Image Database: [Web Link], PAL Face Database from Productive Aging Laboratory, The University of Texas at Dallas: [Web Link]. This dataset is of the dimension 245057 * 4 where first three columns are B,G,R (x1,x2, and x3 features) values and fourth column is of the class labels (decision variable y).


* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Skin+Segmentation)
* __Number of rows__: `r nrow(somerville)`
* __Number of attributes__: `r ncol(somerville) - 1`

__Description of the attributes:__

```{r echo=FALSE}
plot_dist_cols(somerville)
```

##### Tic-Tac-Toe {#Tic-Tac-Toe}

<!-- Binary > Categorical > Less than 10 attributes --> 

This database encodes the complete set of possible board configurations at the end of tic-tac-toe games, where "x" is assumed to have played first. The target concept is "win for x" (i.e., true when "x" has one of 8 possible ways to create a "three-in-a-row"). 


* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Tic-Tac-Toe+Endgame)
* __Number of rows__: `r nrow(tic_tac_toe)`
* __Number of attributes__: `r ncol(tic_tac_toe) - 1`

__Description of the attributes:__

```{r echo=FALSE}
plot_dist_cols(tic_tac_toe)
```


#### 10 or more attributes

### Mixed: categorical and numerical attributes

#### Less than 10 attributes

##### Cesarean

<!-- Binary > Mixed > Less than 10 --> 

* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Caesarian+Section+Classification+Dataset)
* __Number of rows__: `r nrow(caesarian)`
* __Number of attributes__: `r ncol(caesarian) - 1`

__Description of the attributes:__

* 'Age' { 22,26,28,27,32,36,33,23,20,29,25,37,24,18,30,40,31,19,21,35,17,38 } 
* 'Delivery number' { 1,2,3,4 } 
* Delivery time { 0,1,2 } -> {0 = timely , 1 = premature , 2 = latecomer} 
* Heart Problem' { 1,0 } -> {0 = apt, 1 = inept } 

The class:

* Caesarian { 0,1 } -> {0 = No, 1 = Yes } 

```{r echo=FALSE}
plot_dist_cols(caesarian)
```


##### Mammographic masses {#mammographic}

<!-- Binary > Mixed > Less than 10 --> 

Mammography is the most effective method for breast cancer screening 
available today. However, the low positive predictive value of breast 
biopsy resulting from mammogram interpretation leads to approximately 
70% unnecessary biopsies with benign outcomes. To reduce the high 
number of unnecessary breast biopsies, several computer-aided diagnosis 
(CAD) systems have been proposed in the last years.These systems 
help physicians in their decision to perform a breast biopsy on a suspicious 
lesion seen in a mammogram or to perform a short term follow-up 
examination instead. 
This data set can be used to predict the severity (benign or malignant) 
of a mammographic mass lesion from BI-RADS attributes and the patient's age. 
It contains a BI-RADS assessment, the patient's age and three BI-RADS attributes 
together with the ground truth (the severity field) for 516 benign and 
445 malignant masses that have been identified on full field digital mammograms 
collected at the Institute of Radiology of the 
University Erlangen-Nuremberg between 2003 and 2006. 
Each instance has an associated BI-RADS assessment ranging from 1 (definitely benign) 
to 5 (highly suggestive of malignancy) assigned in a double-review process by 
physicians. Assuming that all cases with BI-RADS assessments greater or equal 
a given value (varying from 1 to 5), are malignant and the other cases benign, 
sensitivities and associated specificities can be calculated. These can be an 
indication of how well a CAD system performs compared to the radiologists. 

Class Distribution: benign: 516; malignant: 445 

* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Mammographic+Mass)
* __Number of rows__: `r nrow(mammographic)`
* __Number of attributes__: `r ncol(mammographic) - 1`

__Description of the attributes:__

* BI-RADS assessment: 1 to 5 (ordinal, non-predictive!) 
* Age: patient's age in years (integer) 
* Shape: mass shape: round=1 oval=2 lobular=3 irregular=4 (nominal) 
* Margin: mass margin: circumscribed=1 microlobulated=2 obscured=3 ill-defined=4 spiculated=5 (nominal) 
* Density: mass density high=1 iso=2 low=3 fat-containing=4 (ordinal) 
* Severity: benign=0 or malignant=1 (binominal, goal field!) 

Missing Attribute Values: 
- BI-RADS assessment: 2 
- Age: 5 
- Shape: 31 
- Margin: 48 
- Density: 76 
- Severity: 0 


```{r echo=FALSE}
plot_dist_cols(mammograpic_masses)
```

#####  Vertebral column 2 {#Vertebral-column-2


##### Weight, height, gender ´#Weight-height-gender}
      
#### 10 or more attributes

##### Travel insurance {#Travel-insurance}

A third-party travel insurance servicing company that is based in Singapore.

<!-- Binary > Mixed > 10 or more attributes --> 

* __Source__: [Kaggle](https://www.kaggle.com/mhdzahier/travel-insurance#travel%20insurance.csv)
* __Number of rows__: `r nrow(travel_insurance)`
* __Number of attributes__: `r ncol(travel_insurance) - 1`

__Description of the attributes:__

* Target: Claim Status (Claim.Status)
* Name of agency (Agency)
* Type of travel insurance agencies (Agency.Type)
* Distribution channel of travel insurance agencies (Distribution.Channel)
* Name of the travel insurance products (Product.Name)
* Duration of travel (Duration)
* Destination of travel (Destination)
* Amount of sales of travel insurance policies (Net.Sales)
* Commission received for travel insurance agency (Commission)
* Gender of insured (Gender)
* Age of insured (Age)

```{r}
plot_dist_cols(travel_insurance)
```


### Numeric attributes

#### Less than 10 attributes

##### Banknote authentication {#Banknote}

<!-- Binary > Numeric > Less than 10 attributes --> 

* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/banknote+authentication)
* __Number of rows__: `r nrow(bank_note)`
* __Number of attributes__: `r ncol(bank_note) - 1`

Data were extracted from images that were taken from genuine and forged banknote-like specimens. For digitization, an industrial camera usually used for print inspection was used. The final images have 400x 400 pixels. Due to the object lens and distance to the investigated object gray-scale pictures with a resolution of about 660 dpi were gained. Wavelet Transform tool were used to extract features from images.

__Description of the attributes:__

* variance of Wavelet Transformed image (continuous) 
* skewness of Wavelet Transformed image (continuous) 
* curtosis of Wavelet Transformed image (continuous) 
* entropy of image (continuous) 
* class

```{r}
plot_dist_cols(bank_note)
```

##### Haberman {#Haberman}

<!-- Binary > Numeric > Less than 10 attributes --> 

* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Haberman%27s+Survival)
* __Number of rows__: `r nrow(haberman)`
* __Number of attributes__: `r ncol(haberman) - 1`

The dataset contains cases from a study that was conducted between 1958 and 1970 at the University of Chicago's Billings Hospital on the survival of patients who had undergone surgery for breast cancer.

* Age of patient at time of operation (numerical) 
* Patient's year of operation (year - 1900, numerical) 
* Number of positive axillary nodes detected (numerical) 
* Survival status (class attribute) 
  * 1 = the patient survived 5 years or longer 
  * 2 = the patient died within 5 year

__Description of the attributes:__


```{r}
plot_dist_cols(haberman)
```

##### Skin segmentation {#Skin}

```{r}
plot_dist_cols(skin)
```

#### 10 or more attributes


--------------------------------------------------------------------------------

## Multiclass

### Categorical attributes

#### Less than 10 attributes

##### Balance Scale {#Balance-Scale}

<!-- Multiclass > Categorical > Less than 10 attributes --> 

This data set was generated to model psychological experimental results. Each example is classified as having the balance scale tip to the right, tip to the left, or be balanced. The attributes are the left weight, the left distance, the right weight, and the right distance. The correct way to find the class is the greater of $(left\_distance * left\_weight)$ and $(right\_distance * right\_weight)$. If they are equal, it is balanced.


* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Balance+Scale)
* __Number of rows__: `r nrow(balance_scale)`
* __Number of attributes__: `r ncol(balance_scale) - 1`

__Description of the attributes:__

```{r echo=FALSE}
plot_dist_cols(balance_scale)
```

##### Chess {#Chess}

<!-- Multiclass > Categorical > Less than 10 attributes --> 

```{r}
plot_dist_cols(chess)
```


##### Post operative data {#Post-operative}

<!-- Multiclass > Categorical > Less than 10 attributes --> 

```{r}
plot_dist_cols(post_operative)
```


#### 10 or more attributes

##### Poker hand {#Poker-hand}

<!-- Multiclass > Categorical > 10 or more attributes --> 

```{r echo=FALSE}
plot_dist_cols(poker_hand)
```


### Mixed: categorical and numerical attributes

#### Less than 10 attributes

##### Teaching-assistant

* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Teaching+Assistant+Evaluation)

##### Abalone

Predicting the age of abalone from physical measurements. The age of abalone is determined by cutting the shell through the cone, staining it, and counting the number of rings through a microscope -- a boring and time-consuming task. Other measurements, which are easier to obtain, are used to predict the age. Further information, such as weather patterns and location (hence food availability) may be required to solve the problem. 

From the original data examples with missing values were removed (the majority having the predicted value missing), and the ranges of the continuous values have been scaled for use with an ANN (by dividing by 200).


* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Abalone)
* __Number of rows__: `r nrow(abalone_age)`
* __Number of attributes__: `r ncol(abalone_age) - 1`

__Description of the attributes:__

```{r echo=FALSE}
plot_dist_cols(abalone_age)
```


##### Life expectancy

```{r}
ggplot(life_expectancy, aes(male, female)) + 
  geom_point(aes(color = continent)) 
```



#### 10 or more attributes

### Numeric attributes

#### Less than 10 attributes

##### Life expectancy

```{r}
ggplot(life_expectancy, aes(male, female)) + 
  geom_point(aes(color = continent)) 
```



##### Seeds {#Seeds}

```{r echo=FALSE}
plot_dist_cols(seeds)
```



#### 10 or more attributes

This database encodes the complete set of possible board configurations at the end of tic-tac-toe games, where "x" is assumed to have played first. The target concept is "win for x" (i.e., true when "x" has one of 8 possible ways to create a "three-in-a-row"). 


* __Source__: [UCI Machile Learning Repository](http://archive.ics.uci.edu/ml/datasets/Tic-Tac-Toe+Endgame)
* __Number of rows__: `r nrow(tic_tac_toe)`
* __Number of attributes__: `r ncol(tic_tac_toe) - 1`

__Description of the attributes:__

```{r echo=FALSE}
plot_dist_cols(tic_tac_toe)
```



# Notes

Changes to the original datasets if any:

