---
title: "Distances"
output: html_notebook
---

```{r}
library(tidyverse)
```

For similarity in [0, 1] when 1 is exactly similar the dissimilarity is zero when the similarity is zero, i.e. very different, the dissimilarity is one.

$$s_{ij} = 1 - d_{ij}$$

If the value of similarity has range of -1 to +1 and the dissimilarity is measured with range 0 and 1 then:

$$s_{ij} = 1 - 2d_{ij}$$

because when the dissimilarity is one i.e. very different the similarity is minus one and when the dissimilarity is zero i.e. very similar the similarity is 1-


## Distance for binary variables


Given two binary vectors, $x$ and $y$, of 0s and 1s:

* p = number of variables that are positive (1) for both instances
* q = number of variables that are positive (1) for the $i_th$ object and negative (0) for the $j_th$ object
* r = number of variables that are negative (0) for the $i_th$ object and positive (1) for the $j_th$ object
* s = number of variables that are positive (1) for both instances

* $t = p + q + r + s$

| i / j | Yes | No |
|-------|-----|----|
| Yes   | p   | q  |
| No    | r   | s  |

```{r}
i <- factor(c("yes", "no", "yes", "no", "yes"), levels = c("yes", "no"))
j <- factor(c("no", "yes", "no", "no", "yes"), levels = c("yes", "no"))
```

```{r}
table(i, j)
```

```{r}
createTable <- function(i, j) {
  vtable <- list()
  vtable$table <- table(i, j)
  vtable$p <- vtable$table[1, 1]
  vtable$q <- vtable$table[1, 2]
  vtable$r <- vtable$table[2, 1]
  vtable$s <- vtable$table[2, 2]
  vtable
}
```


## Simple matching distance

Useful when both positive and negative values carry equal information. Counts the number of times that both are different (one positive and the other negative).

$$d_{ij} = \frac{q+r}{p + q + r + s} = \frac{q+r}{t}$$

```{r}
simple_matching_distance <- function(i, j) {
  d <- createTable(i, j)
  t <- d$p + d$q + d$r + d$s
  return((d$q + d$r) / t)
}
```


## Jaccard's distance

$$d_{ij} = \frac{q+r}{p + q + r}$$

## Hamming distance

Measures the level of disagreement between two vectors. Count the number of digits in positions where they have a different digit. Distance is higher for values with bigger number of categories.

$$d_{ij} = q + r$$

## Simple matching coefficient

Useful when both positive and negative values carry equal information. Counts the number of times that both are equals (both positive or both negative)

$$d_{ij} = \frac{p+s}{p + q + r + s} = \frac{p+s}{t}$$

## Jaccard's coefficient

$$d_{ij} = \frac{p}{p + q + r} = \frac{p}{p + q + r}$$

# Distance for nominal variables


# Distance for ordinal variables

## Normalized Rank Transformation

## Spearman Distance

## Footrule Distance

## Kendall Distance

## Cayley Distance

## Hamming Distance

## Ulam Distance

## Chebyshev/Maximum distance

## Miskowski Distance


# Distance for quantitative variables


# Distance function

The native `dist` funtion in the `stats` package computes and returns the distance matrix computed by using the specified distance measure to compute the distances between the rows of a data matrix.

The available distances are:

* euclidean:

$$d(x,y) =\sqrt{\sum{(x_i - y_i)^2}}$$

* maximum:
* manhattan:
* canberra:

$$\sum{\frac{(x_i - y_i)}{x_i + y_i}}$$

* binary:

The distance is the proportion of bits in which only one is on amongst those in which at least one is on.

* minkowski:

$$$$


