---
title: "Thesis"
date: "`r Sys.Date()`"
author: "Noelia Rico"
output:
  rmdformats::readthedown:
    highlight: kate
---


```{r knitr_init, message=TRUE, warning=TRUE, cache=FALSE, include=FALSE}
library(knitr)
library(rmdformats)
library(tidyverse)
library(kableExtra)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

* [Ranking rules: `consensus`](#consensus)
  * [Scoring ranking rules](#scoring-ranking-rules)
    * Plurality(#plurality)
    * k-rules(#krules)
    * Borda count(#borda)
* [Distances](#distances)
  * [Categorical features](#categorical-features)
  * [Numerical features](#numerical-features)
  * [Mixed features](#mixed-features)
* Algorithms
  * [`dknn`](#dknn)
    * [Sets of distances](#sets)
  * [`rknn`](#rknn)
* [Datasets](#datasets)
* [Examples](#examples)


#  Ranking rules: `consensus` {#consensus}

## Scoring ranking rules {#scoring-ranking-rules}

### Plurality {#plurality}


### k-rules {#k-rules}
### Borda count {#borda}
# Distances {#distances}
## Categorical features {#categorical-features}
## Numerical features {#numerical-features}
## Mixed features {#mixed-features}
# Algorithms
## `dknn` {#dknn}
### Sets of distances  {#sets}
## `rknn` {#rknn}
# Datasets {#datasets}


```{r child = '../Datasets.Rmd'}
```


# Examples {#examples}

## The `mini_iris` dataset

### Manhattan distance with `mini_iris` 

### Euclidean distance with `mini_iris` 


<div style="font-family:courier;">
  Train dknn k = 3, distance = euclidean, ties = randomly
  nrow(train) = 9 and nrow(test) = 3 
  </hr></br>
  
  <mark style="font-family:courier; background-color: #fbebf0">Matrix of distances:</mark>


</div>

```{r  echo=FALSE}
m1 <- tribble(
~test, ~X1, ~X2, ~X3, ~X5, ~X6, ~X7, ~X9, ~X10, ~X11,
"X4",  2.144761, 1.627882, 0.7141428, 4.5607017, 3.9648455, 3.8923001, 4.160529, 6.522270, 4.2731721,
"X8",  3.491418, 3.295451, 3.6687873, 0.9643651, 0.4358899, 0.3464102, 1.104536, 2.917190, 0.7937254,
"X12", 4.713809, 4.570558, 4.9909919, 0.8831761, 1.2083046, 1.2369317, 1.195826, 1.838478, 0.8366600)
m1 %>% kable(align = "c") %>% kable_styling(c("condensed", "bordered"))
```

<div>
  <mark style="font-family:courier; background-color: #fbebf0">Ranking for each instance:</mark>


</div>


```{r  echo=FALSE}
m2 <- tribble(
~testtrain, ~X1, ~X2, ~X3, ~X5, ~X6, ~X7, ~X9, ~X10, ~X11,
"X4", 3, 2, 1, 8, 5, 4, 6, 9, 7,
"X8", 8, 7, 9, 4, 2, 1, 5, 6, 3,
"X12", 8, 7, 9, 2, 4, 5, 3, 6, 1)
```

```{r echo=FALSE}
# colors <- c("#562424", "#6d3636", "#924444", "#a94c4c", "#c17171",
#             "#f45ca2", "#ffbdd3", "#ffd7e4", "#fff0f5", "#ffffff")
            #"#FF9AA5", "#B5EAD7", "#FFDAC1", "#EBCEED", "#F0DEFD")

colors <- c("#1d060c", "#3e0c1a", "#6f162e", "#a02043", "#c12751", "#da4870", "#e47996", "#eeaabc", "#f8dbe3", "#fefcfc")

colors <- factor(1:10, labels = colors, levels = 1:10)
m2 %>%
  mutate_at(vars(-testtrain), .funs = ~cell_spec(., color = "white", bold = T, background = colors[.], font_size = 14)) %>%
  kable(escape = F, align = "c") %>% kable_styling(c("condensed", "bordered"))
```

```
Train dknn k = 3, distance = euclidean, ties = randomly
nrow(train) = 9 and nrow(test) = 3 





Predict... Choosing a label [method =  randomly , k =  3] for the instance X4: 

setosa     setosa     setosa versicolor versicolor versicolor  virginica  virginica  virginica 
    3          2          1          8          5          4          6          9          7 
    
    
setosa > setosa > setosa > versicolor > versicolor > virginica > virginica > versicolor > virginica 


--> Selected values:
setosa setosa setosa

--> Probabilities:
    setosa versicolor  virginica 
         1          0          0 

The label for this instance is: setosa 

Predict... Choosing a label [method =  randomly , k =  3 ] for the instance X8: 
     
setosa     setosa     setosa versicolor versicolor versicolor  virginica  virginica  virginica 
8          7          9          4          2          1          5          6          3 


versicolor > versicolor > virginica > versicolor > virginica > virginica > setosa > setosa > setosa 

--> Selected values:
versicolor versicolor virginica 

--> Probabilities:
    setosa versicolor  virginica 
 0.0000000  0.6666667  0.3333333 

The label for this instance is: versicolor 

Predict... Choosing a label [method =  randomly , k =  3 ] for the instance X12: 

setosa     setosa     setosa versicolor versicolor versicolor  virginica  virginica  virginica 
8          7          9          2          4          5          3          6          1 

virginica > versicolor > virginica > versicolor > versicolor > virginica > setosa > setosa > setosa 

--> Sure values:
versicolor  virginica 
         2          1 

--> Tied values:
virginica 
        3 

Solving the ties... randomly

--> Number of elements to select randomly: 1 

--> Selected values:
[1] versicolor virginica  virginica 
Levels: setosa versicolor virginica
times
    setosa versicolor  virginica 
 0.0000000  0.3333333  0.6666667 

The label for this instance is: virginica 
[1] "setosa"     "versicolor" "virginica" 

> sink("iris_manhattan_randomly")
```

### Chebyshev distance with `mini_iris` 

### mini_zoo
